% !TEX root = main.tex

% TODO:
% REMARK:

\section{Asymmetry Bias}
\label{sec:AsymBias}

	In the standard model(SM), the $A_{cp}$ of $t\bar{t}$ and other background are expected to be zero, that is to say, there is no asymmetry. However, the $A'_{cp}$ value may be affected by the reconstructing and detector demonstrating, and also the particles' characteristic may interact with detector, so the $A'_{cp}$ might be different from the real $A_{cp}$. And the reconstruction effects from the detector can be studied by simulation sample. Also, the detector and reconstruction bias is expected to be the major systematic uncertainty of the analysis.

	The best way to estimate the detector and reconstruction issue is to see the $A'_{cp}$ bias of a sample which supposes to be zero in $A_{cp}$. And then, the standard deviation(error) of $A'_{cp}$ is taken as the detector and reconstruction bias. The sample needs to be irrelavent with the target signal of this analysis -- $t\bar{t}$ because we expect the possible source of asymmetry is in $t\bar{t}$. Accordingly, the SR background sample is appropriate to be studied for the detector and reconstruction bias since it is supposed to be without $A_{cp}$ and it is nothing relative to the signal in the analysis($t\bar{t}$). However, the SR background sample has low statistics. Therefore, the method in 8TeV analysis is using the W+jets-dominant CR data sample as the sample supposed to be without $A_{cp}$, because the W+jets CR data sample is used to data-driven the SR background sample. Yet, in this analysis, we use the analyzed data itself and a fake data method to doing this study. It is advatage of using SR data itself that the statistics is more than CR data and that the W+jets-dominant CR smaple still includes over $10\%$ $t\bar{t}$. And the chapter is to introduce the fake data method to calculate the detector and reconstruction bias.

	\subsection{Asymmetry in simulation sample}
	\label{ssec:Asym_in_sim}

	There are the $A'_{cp}$ of $t\bar{t}$ in SR with 3 different reconstruction results($\chi^2_{min}$, MVA-A, MVA-B). It is expected to have no asymmetry.



	\subsection{Events changing method}
	\label{ssec:evts_changing}

\FloatBarrier
